An Accurate Model for SARS-CoV-2 Pooled RT-PCR Test Errors

### 2021-09-09 paper.tex
after uris commentz

Furthermore, an especially important consideration in designing
pooling schemes is explicitly taking the intrinsic PCR error rates
into account. As we have demonstrated above, analyzing the expected
error rates of pooling schemes under a realistic probabilistic error
model is readily achievable. Designing pooling schemes which optimize
testing while accounting for error rates is, however, far from
trivial. Nonetheless, various algorithms explicitly incorporate error
rates into their pooling optimization processes (REFS), including a
recent study by our group which employed the herein described error
model \cite{DOPE}.  In our proposed algorithm, we have used a Bayesian
experimental design criterion to create an algorithm which iteratively
performs pooling schemes, updating its information based on previous
results. In doing so, our pooling scheme shows potential in terms of
both reducing false-negative rates, as well as increasing efficiency,
although it has not yet been implemented in real-world settings.

>>>>

Furthermore, an especially important consideration in designing
pooling schemes is explicitly taking the intrinsic RT-PCR error rates
into account. As we have demonstrated above, analyzing the expected
error rates of pooling schemes under a realistic error
model is readily achievable. Designing pooling schemes which optimize
testing while accounting for error rates is, however, considerably more involved.
Nonetheless, various algorithms explicitly incorporate error
rates into their pooling optimization processes \cite{BayesianDorfman, Kim, OptimalDorfmanPool}, including a
recent study by our group which employed the herein described error
model \cite{DOPE}.  In our proposed algorithm, we have used a Bayesian
experimental design criterion to create an algorithm which iteratively
performs pooling, updating its information based on previous
results. In doing so, our pooling scheme shows potential in terms of
both reducing false-negative and false-positive rates, as well as increasing efficiency,
although it has not yet been implemented in real-world settings.
